\citace{albayrakDuplicateProductRecord2022a}{Albayrak, 2022}{\autor{Albayrak, Osman Semih; Aytekin, Tevfik; Kalaycı, Tolga Ahmet} \nazev{Duplicate product record detection engine for e-commerce platforms}. Expert Systems with Applications. 2022, roč. 193. ISSN 0957-4174. Dostupné z: \url{https://www.sciencedirect.com/science/article/pii/S0957417421017073}.}

\citace{bessProblemDuplicateMismatched2024}{Bess, 2024}{\autor{Bess, Oleg} \nazev{The problem with duplicate and mismatched patient records} [online]. 2024 [cit. 2025-02-09]. Dostupné z: \url{https://www.physicianspractice.com/view/the-problem-with-duplicate-and-mismatched-patient-records}.}

\citace{brown8ProblemsThat2019}{Brown, 2019}{\autor{Brown, Forrest} \nazev{8 Problems That Result from Data Duplication • Profisee} [online]. 2019 [cit. 2025-02-09]. Dostupné z: \url{https://profisee.com/blog/8-business-process-problems-that-result-from-data-duplication/}.}

\citace{christenDataMatchingConcepts2012}{Christen, 2012}{\autor{Christen, Peter} \nazev{Data matching: concepts and techniques for record linkage, entity resolution, and duplicate detection}. Berlin Heidelberg, 2012. 270~s. ISBN 978-3-642-43001-5 978-3-642-31163-5.}

\citace{clevermapsLocationInsightsBusiness2024}{CleverMaps, 2024}{\autor{CleverMaps} \nazev{Location Insights for Business} [online]. 2024 [cit. 2024-04-28]. Dostupné z: \url{https://www.clevermaps.io}.}

\citace{draisbachChoosingThresholdsDuplicate2013}{Draisbach, 2013}{\autor{Draisbach, Uwe; Naumann, Felix} \nazev{On Choosing Thresholds for Duplicate Detection} [online]. 2013 [cit. 2024-04-28]. Dostupné z: \url{https://hpi.de/oldsite/fileadmin/user\_upload/fachgebiete/naumann/publications/PDFs/2013\_draisbach\_on.pdf}.}

\citace{elahiWhyDataDuplicates2021}{Elahi, 2021}{\autor{Elahi, Ehsan} \nazev{Why Data Duplicates Exist and How to Get Rid of Them? - Data Ladder Data Duplicates: Why Do They Exist and How to Eliminate Them?} [online]. 2021 [cit. 2025-02-09]. Dostupné z: \url{https://dataladder.com/why-data-duplicates-exist-how-to-get-rid-of-them/}.}

\citace{esriGISDictionary2024}{Esri, 2024}{\autor{Esri} \nazev{GIS Dictionary} [online]. 2024 [cit. 2024-04-28]. Dostupné z: \url{https://support.esri.com/en-us/gis-dictionary/search}.}

\citace{evensenEntityResolutionIntroduction2024}{Evensen, 2024}{\autor{Evensen, Adrian} \nazev{Entity Resolution — An Introduction} [online]. 2024 [cit. 2024-10-13]. Dostupné z: \url{https://medium.com/@adev94/entity-resolution-an-introduction-fb2394d9a04e}.}

\citace{googletrendsGoogleTrends2025}{Google Trends, 2025}{\autor{Google Trends} \nazev{Google Trends} [online]. 2025 [cit. 2025-11-21]. Dostupné z: \url{https://trends.google.com/trends/explore?date=today\%205-y\&q=data\%20matching,entity\%20resolution,record\%20linkage\&hl=cs}.}

\citace{heavy.aiWhatGeodataDefinition2024}{HEAVY.AI, 2024}{\autor{HEAVY.AI} \nazev{What is Geodata? Definition and FAQs} [online]. 2024 [cit. 2024-08-18]. Dostupné z: \url{https://www.heavy.ai/technical-glossary/geodata}.}

\citace{howardPhoneticSpellingAlgorithm2020}{Howard, 2020}{\autor{Howard, James P., II} \nazev{Phonetic Spelling Algorithm Implementations for R}. . 2020, roč. 95. ISSN . Dostupné z: \url{https://doi.org/10.18637/jss.v095.i08}.}

\citace{huyenDesigningMachineLearning2022}{Huyen, 2022}{\autor{Huyen, Chip} \nazev{Designing machine learning systems: an iterative process for production-ready applications}. Beijing Boston Farnham Sebastopol Tokyo, 2022. 367~s. ISBN 978-1-0981-0796-3.}

\citace{jurafskySpeechLanguageProcessing2025}{Jurafsky, 2025}{\autor{Jurafsky, Daniel; Martin, James H.} \nazev{Speech and Language Processing: An Introduction to Natural Language Processing, Computational Linguistics, and Speech Recognition, with Language Models}. , 2025. ~s. ISBN .}

\citace{kerasKerasDocumentationGetting2024}{Keras, 2024}{\autor{Keras} \nazev{Keras documentation: Getting started with Keras} [online]. 2024 [cit. 2024-04-29]. Dostupné z: \url{https://keras.io/getting\_started/}.}

\citace{mcclainPythonGeospatialData2023}{McClain, 2023}{\autor{McClain, Bonny P.} \nazev{Python for geospatial data analysis: theory, tools, and practice for location intelligence}. Beijing Boston Farnham Sebastopol Tokyo, 2023. 262~s. ISBN 978-1-0981-0479-5.}

\citace{mcgregorPracticalPythonData2022}{McGregor, 2022}{\autor{McGregor, Susan E.} \nazev{Practical Python data wrangling and data quality}. Sebastopol, CA, 2022. 395~s. ISBN 978-1-4920-9150-9.}

\citace{naumanIntroductionDuplicateDetection2022}{Nauman, 2022}{\autor{Nauman, Felix; Herschel, Melanie} \nazev{An Introduction to Duplicate Detection}. , 2022. 84~s. ISBN 978-3-031-01835-0.}

\citace{newvantagepartnersGlobalStateData2024}{NewVantage Partners, 2024}{\autor{NewVantage Partners} \nazev{Global state of data/analytics investment 2023} [online]. 2024 [cit. 2025-02-12]. Dostupné z: \url{https://www.statista.com/statistics/1453262/global-state-of-data-analytics-investment/}.}

\citace{pasekMQDDPretrainingMultimodal2022}{Pašek, 2022}{\autor{Pašek, Jan; Sido, Jakub; Konopík, Miloslav; Pražák, Ondřej} \nazev{MQDD -- Pre-training of Multimodal Question Duplicity Detection for Software Engineering Domain} [online]. 2022 [cit. 2024-04-29]. Dostupné z: \url{https://www.researchgate.net/publication/359518098\_MQDD\_--\_Pre-training\_of\_Multimodal\_Question\_Duplicity\_Detection\_for\_Software\_Engineering\_Domain\#fullTextFileContent}.}

\citace{quantexaWhatDataMatching2024}{Quantexa, 2024}{\autor{Quantexa} \nazev{What is Data Matching \& How Does it Work?} [online]. 2024 [cit. 2024-11-13]. Dostupné z: \url{https://www.quantexa.com/resources/data-matching/}.}

\citace{scikit-learndevelopersScikitlearnMachineLearning2024}{scikit-learn developers, 2024}{\autor{scikit-learn developers} \nazev{scikit-learn: machine learning in Python — scikit-learn 1.4.2 documentation} [online]. 2024 [cit. 2024-04-30]. Dostupné z: \url{https://scikit-learn.org/stable/index.html}.}

\citace{shearerHandsonEntityResolution2024}{Shearer, 2024}{\autor{Shearer, Michael} \nazev{Hands-on entity resolution: a practical guide to data matching with python}. Beijing Boston Farnham Sebastopol Tokyo, 2024. 1~s. ISBN 978-1-0981-4848-5 978-1-0981-4845-4.}

\citace{stepanenkoWhatEntityResolution2024}{Stepanenko, 2024}{\autor{Stepanenko, Roman} \nazev{What is Entity Resolution} [online]. 2024 [cit. 2024-11-14]. Dostupné z: \url{https://recordlinker.com/what-is-entity-resolution/}.}

\citace{tejadaLearningObjectIdentification2002}{Tejada, 2002}{\autor{Tejada, Simon} \nazev{Learning Object Identification Rules for Information Extraction}. Austin, TX, 2002. . .  Dostupné z: \url{https://usc-isi-i2.github.io/papers/tejada02-thesis.pdf}.}

\citace{tensorflowMachineLearningEducation2024}{TensorFlow, 2024}{\autor{TensorFlow} \nazev{Machine learning education | TensorFlow} [online]. 2024 [cit. 2024-04-29]. Dostupné z: \url{https://www.tensorflow.org/resources/learn-ml}.}

\citace{tiloresFuzzyMatchingAlgorithms2023}{Tilores, 2023}{\autor{Tilores} \nazev{Fuzzy Matching Algorithms for Data Deduplication and Linking} [online]. 2023 [cit. 2024-04-28]. Dostupné z: \url{https://tilores.io/fuzzy-matching-algorithms}.}

\citace{winklerMatchingRecordLinkage2014}{Winkler, 2014}{\autor{Winkler, William} \nazev{Matching And Record Linkage}. Wiley Interdisciplinary Reviews: Computational Statistics. 2014, roč. 6. ISSN 9780471598527. Dostupné z: \url{}.}

\citace{wittenDataMiningPractical2017}{Witten, 2017}{\autor{Witten, Ian H.; Frank, Eibe; Hall, Mark A.; Pal, Christopher J.} \nazev{Data mining: practical machine learning tools and techniques}. Amsterdam Boston Heidelberg London New York Oxford Paris San Diego San Francisco Singapore Sydney Tokyo, 2017. 621~s. ISBN 978-0-12-804291-5.}

